Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-08-16 Tex/elsevier/reply Solar Energy AUG 2019.tex
Solar Energy journal reply R2

We thank you for asking us to comply with your reviewers' reports. 
We are submitting a revised version of our manuscript entitled 
``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro. 
This revised version carefully addresses each comment provided 
by the reviewers, as suggested in your original decision letter. 
In particular, our reply letter describes all modifications we made 
to our manuscript and the respective responses to the comments 
raised by the reviewers.

@@

The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions, which helped us significantly improve the quality of our manuscript.

According to the associate editor and reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text.

Our responses  to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed along our manuscript.

We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication in {\bf Solar Energy}.

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. Indeed, we had to rewrite the highlights doc fileit summarizes what was intended to be studied in this manuscript. Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modeling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript. Regarding Figure 2, we fixed it as recommended by the reviewer. Moreover, we applied the same procedure to voltage $V$, in order to keep consistency throughout our manuscript.

>>>>

We thank you for asking us to comply with your reviewers' reports. 
We are submitting a revised version of our highlights file from the entitled paper  
``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro. 
This revised version carefully addresses the comment provided 
by the reviewers, as suggested in your original decision letter. 
In particular, our reply letter describes all modifications we made 
to our highlights file and the respective response to the comments 
raised by the reviewer.

@@

The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions related to the highlights file, which helped us significantly improve the quality of our material.

According to the associate editor and reviewers' comments, our highlights file has been carefully modified and rewritten.

Our responses  to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed.

We hope those modifications in our highlights file and also our responses are sufficient to make our work suitable for publication in {\bf Solar Energy}.

@@

\begin{resposta} 
We thank the reviewers for this insightful comment and suggestion. Indeed, we had to rewrite the highlights doc file to comply with the correct expectation from {\bf Solar Energy} journal.

Now our new highlights files states:
\begin{itemize}
\item Verification can be effective to validate stand-alone solar photovoltaic systems
\item Automated verification method can detect design errors better than simulation
\item ESBMC can produce better performance and soundness among automated verifiers
\end{itemize}

Compared with the original and not suitable:
\begin{itemize}
\item Approach detect design errors which are not easily detected by other approaches
\item Algorithm that implements the automated verification method 
\item Formal checking of the sizing and the operation of a given stand-alone PV system
\item Comparative of three state-of-the-art model checkers in five real case studies
\end{itemize}
